On the analytic structure of the linear response susceptibility in open systems

### 2018-03-16 AnalyticStructure_main.tex
update

.....

@@

This analysis, carried out starting from the representation of the linear response functional in terms of fluctuation states, evidences some general properties of the linear response. 
In the next sections we will reformulate an analogous procedure directly looking at the susceptibility. This analysis lead us to the core of the paper, namely the description of the
analytical structure of the linear response susceptibility.

@@

Inizio a mettere le formule da usare...forse...

Liouville equation:
\be\lb{LiouvillianRhopomegaDef1}
\left(\omega - \Liouv\right) \dm'(\omega) =  \commutator{\op\Phi(\omega)}{\dmnot}\;,\;\; 
\Liouv = \Liouvnot + \coupl \;.
\ee
% by introducing the \emph{coupling}
% superoperator:
% \be\lb{couplingSopDef1}
% \coupl = 
% \int \dd \r \dd \r' \commutator{\frac{\delta\hnot}{\delta \rho_0(\r,\r')}}{\dmnot}
% \trace{\cdot \ket{\r} \bra{\r'}} \;,
% \ee
Excitation operators as eigenstates of the Liouvillian:
\be
\Liouv \op E = E \op E \;, \qq
 \op{\tilde E} \Liouv = E \op{\tilde E}
\ee

>>>>

State something about the assessment of physical reliability for a ground state calculation. Some comment on the setup independence of the results. Introduce the correspondence
between localization properties and observable behavior or physicality. State the, at the present days, similar consideration for the results of linear response are still 
missing...

The basic motivation at the basis of the analysis discussed in this paper is to address to following question: which are the requirement that a computational setup has to
satisfy in order to be able to provide physical results for a linear response calculation? Here with physical we meant that they depend only on the features of the system under
inspection and on the perturbation acting on it. Physical results are unaffected by computational parameters, like the dimension of the computational domain or the nature of
the basis set used to perform the calculations.

To answer to this question we investigate the properties of the susceptibility, which represents the fundamental object in the contest of linear response.

@@

%This analysis, carried out starting from the representation of the linear response functional in terms of fluctuation states, evidences some general properties of the linear response. 
%In the next sections we will reformulate an analogous procedure directly looking at the susceptibility. This analysis lead us to the core of the paper, namely the description of the
%analytical structure of the linear response susceptibility.

@@

The analysis carried out starting from the representation of the linear response functional in terms of fluctuation states, has evidenced some general properties of the linear response
for open systems. In particular, by analyzing the asymptotic behavior of fluctuation states in long range limit, we have showed that they exhibit a bound-state character in the regime  
$\omega<|\eps_h|$. consequently we have argued that the linear response functional, in the same $\omega$ range, provides a setup-independent result with a modest computational effort.

Now we reformulate an analogous analysis looking at the susceptibility superoperator, implicit defined through \eqref{SusceptibilityDef1}. This approach leads to the concept of \emph{excitation 
operators}, defined through a self-consistent operator eigenvalue equation. Excitations behave as singularity of the susceptibility operator and their knowledge provides a deeper insight 
into the analytic structure of the linear response.

The starting point of this analysis is represented by the Liouville equation for the response density operator:
\be\lb{LiouvillianRhopomegaDef1}
\left(\omega - \Liouv\right) \dm'(\omega) =  \commutator{\op\Phi(\omega)}{\dmnot} \;.
\ee
Using the spectral decomposition of the resolvent of the Liouvillian we have:
\be\lb{RhopExcitationDef1}
\sop{{\cal R}}(\omega) \cdot   =
\sint\dd E \, \op E
\frac{\trace{\opskew{\tilde E}\cdot}}{\omega-E} \;,
\ee
with $\opskew{O} = \commutator{\op O}{\dmnot}$. 
Excitation operators as eigenstates of the Liouvillian (keep left and right different or not?):
\be\lb{ExcitationOperatorsDef1}
\Liouv \op E = E \op E \;, \qq
 \op{\tilde E} \Liouv = E \op{\tilde E}
\ee
We can express excitation operators as follows:
\begin{align}\lb{ExcitationOperatorsDef2}
\op E &= \sum_p \left( \ket{\phi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^E_p}\right)\;, \nn \\
\op {\tilde E} &= \sum_p \left( \ket{\psi_p} \tbra{\phi^E_p} + \tket{\chi^E_p}\bra{\psi_p} \right)\;.
\end{align}
